\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-29 Paper/Paper.tex
Update criteria to include abbr.s; edit data prep section

	First, we acquire data from publicly available online datasets. For abnormities that we have no data of, we search for images on Google Image. The numbers of images acquired from each data source are shown in Tables \ref{tb:OCT_source} and \ref{tb:Fundus_source}.

@@

	Then, for OCT images that have less than 1000 images, we use Cycle-GAN to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy images to abnormity images, and use it to generate new abnormity images. We manually eliminate generated images that look obviously wrong. The elimination rate is shown in Table~\ref{tb:cycleGAN_number}. We only used Cycle-GAN to generate OCT images because generated fundus images are too blurry and do not display the target abnormities.

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{ccccc}
				\caption{OCT images CycleGAN elimination rate}
				\label{tb:cycleGAN_number}\\
				\toprule
				Abnormity&Original&Generated&Eliminated&Elimination Rate\\
				\midrule
				CSC   &134&3000&1270&42.333\% \\
				ERM   &19 &3000&1069&35.633\% \\
				MH    &130&3000&1189&39.633\% \\
				Mactel&29 &3000&1100&36.667\% \\
				RP    &133&3000&1077&36.900\% \\
				ST    &23 &3000&418 &13.933\% \\
				\bottomrule
			\end{longtable}
		}
	}

	TEXT: transforms for OCT
	for train: copy, flip, randomcomb1
	for test: copy, flip, randomcomb2 -> explain truthfulness
	explain differences between train and test, OCT and fundus

@@

	TEXT: intro to five-fold train/valid (reason for using this?)

	TEXT: starting point of fine-tuning
	prevent overfitting

	TEXT: crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
	conda, PyTorch;
	desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM

>>>>

	First, we acquire data from publicly available online datasets. For abnormities with no data found, we search for images on Google Image. The numbers of images acquired from each data source are shown in Table~\ref{tb:OCT_source} and Table~\ref{tb:Fundus_source}. For the links of the images from Google Image, please refer to ``Appendix''.

@@

	Then, for OCT abnormities with less than 1000 images, we use Cycle-GAN to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images. We manually eliminate generated images that look obviously wrong. The elimination rates are shown in Table~\ref{tb:cycleGAN_number}. We did not use Cycle-GAN to generate fundus images because generated fundus images are too blurry and do not display the desired abnormities.

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{ccccc}
				\caption{OCT images CycleGAN elimination rates}
				\label{tb:cycleGAN_number}\\
				\toprule
				Abnormity&Original&Generated&Eliminated&Elimination Rate\\
				\midrule
				CSC   &134&3000&1270&42.333\% \\
				ERM   &19 &3000&1069&35.633\% \\
				MH    &130&3000&1189&39.633\% \\
				Mactel&29 &3000&1100&36.667\% \\
				RP    &133&3000&1077&36.900\% \\
				ST    &23 &3000&418 &13.933\% \\
				\bottomrule
			\end{longtable}
		}
	}

	We separate the images, including generated images, into training and testing datasets. We implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images. The rotation is only applied to images in the train dataset. Eventually, we get 5000 train images and 500 test images for each OCT abnormity, and 3000 train images and 300 test images for each fundus abnormity.

@@

	We

	TEXT: intro to five-fold train/valid (reason for using this?)
	TEXT: crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
	conda, PyTorch;
	desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM
